GEE models

### 2017-07-11 doc/manuscript.Rmd
sample.outcome -> pct_outcome$n
removed extra empty lines
s/echo/include
inline results of significant FA from GEE

```{r setup, echo=FALSE}
devtools::load_all('.')
set_options()
```

@@

ds0yr <- dplyr::filter(project_data, VN == 0)
female <- calc_npercent(ds0yr$Sex, 'Female')
european <- calc_npercent(ds0yr$Ethnicity, 'European')
famhist <- calc_npercent(ds0yr$FamHistDiab, 'Yes')
est_gee <- gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    calc_gee_magnitude()
```

@@

Note: Values are in median (IQR), mean (SD), and n (%). The proportion of ethnic
and sex groups did not change over the 6 years. Outcome variables sample size
ranges from `r sample.outcomes` over the 3 visits.

>>>>

```{r setup, include=FALSE}
devtools::load_all('.')
set_options()
```

@@

ds0yr <- dplyr::filter(project_data, VN == 0)
female <- calc_npercent(ds0yr$Sex, 'Female')
european <- calc_npercent(ds0yr$Ethnicity, 'European')
famhist <- calc_npercent(ds0yr$FamHistDiab, 'Yes')
est_gee <- gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    calc_gee_magnitude()

sig_fa_unadj <- gee_results %>% 
    dplyr::filter(model == "Unadjusted", p.value < 0.05) %>% 
    dplyr::select(Yterms, Xterms, unit) %>% 
    dplyr::mutate(Xterms = ifelse(Xterms == "Total", "total NEFA", as.character(Xterms)))
sig_fa_adj <- gee_results %>% 
    dplyr::filter(model == "Adjusted", p.value < 0.05) %>% 
    dplyr::select(Yterms, Xterms, unit) %>% 
    dplyr::mutate(Xterms = ifelse(Xterms == "Total", "total NEFA", as.character(Xterms)))
```

@@

Note: Values are in median (IQR), mean (SD), and n (%). The proportion of ethnic
and sex groups did not change over the 6 years. Outcome variables sample size
ranges from `r chg_outcomes$n` over the 3 visits.
